Analysing Constraint Grammars with a SAT-solver

### 2016-03-09 paper/lrec/lrec2016_listenmaa_claessen.tex
add anonymous reviewers to acknowledgments

\abstract{
We describe a method for analysing Constraint Grammars (CG) that can detect internal conflicts and redundancies in a given grammar, without the need for a corpus. The aim is for grammar writers to be able to automatically diagnose, and then manually improve their grammars. Our method works by automatically translating the given grammar into logical constraints that are analysed by a SAT-solver. We have evaluated our analysis on a number of non-trivial grammars and found inconsistencies.
\newline 
\Keywords{Constraint Grammar, SAT, Grammar Analysis} }

@@

\section*{Acknowledgments}
We thank Eckhard Bick for the idea to apply SAT to CG analysis, and Francis Tyers for insightful discussions.

>>>>

\abstract{
We describe a method for analysing Constraint Grammars (CG) that can detect internal conflicts and redundancies in a given grammar, without the need for a corpus. The aim is for grammar writers to be able to automatically diagnose, and then manually improve their grammars. Our method works by translating the given grammar into logical constraints that are analysed by a SAT-solver. We have evaluated our analysis on a number of non-trivial grammars and found inconsistencies.
\newline 
\Keywords{Constraint Grammar, SAT, Grammar Analysis} }

@@

\section*{Acknowledgments}
We thank Eckhard Bick for the idea to apply SAT to CG analysis, and Francis Tyers for insightful discussions, as well as our anonymous reviewers for comments and suggestions.
